---
title: "Description of CFGL package"
author: "Yafei Lyu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
theme: united
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Condition-adaptive fused graphical lasso (CFGL) is a data-driven approach to incorporate 
condition specificity in the estimation of co-expression networks. More details can be found in 
 https://www.biorxiv.org/content/early/2018/03/28/290346


The CFGL package is an implementation of condition-adaptive fused graphical lasso method. It 
allows you:

- Build co-expression network for multiple biological conditions simultaneously
- Build tissue-specific or shared networks
- Visualize co-expression network and get hub genes

This document introduces you an example of CFGL application. It shows you how to build a co-
expression network with CFGL using multi-condition expression data. Also, several functions for 
co-expression network exploratory analysis and visualization are presented.

## Install the package

The package can be installed from Github. R package **devtools** is required. By specifying 
`build_vignettes = T` to create a vignettes for the CFGL. Note that the CFGL depends two other 
packages: **glmnet** and **igraph**.

```{r, message = FALSE,eval = FALSE}
library(devtools)
install_github("Yafei611/CFGL", build_vignettes = T)
library(CFGL)
```